### 2021-08-10 README.Rmd
standardize distribution naming

```{r, message = FALSE, warning = FALSE}
null_distn <- gss %>%
   specify(age ~ partyid) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
```

@@

```{r viz, message = FALSE, warning = FALSE, eval = FALSE}
visualize(null_distn) +
  shade_p_value(obs_stat = F_hat, direction = "greater")
```

@@

```{r, message = FALSE, warning = FALSE}
null_distn %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
```

>>>>

```{r, message = FALSE, warning = FALSE}
null_dist <- gss %>%
   specify(age ~ partyid) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
```

@@

```{r viz, message = FALSE, warning = FALSE, eval = FALSE}
visualize(null_dist) +
  shade_p_value(obs_stat = F_hat, direction = "greater")
```

@@

```{r, message = FALSE, warning = FALSE}
null_dist %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
```
